---
title: "Introduction to fullMatrix"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to fullMatrix}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(fullMatrix)
```

**Overview**

The fullMatrix package helps convert a 10X Genomics-style sparse matrix into a dense matrix in data.table format, which is easier to manipulate for downstream analysis in R.

This vignette walks through how to use the main function read_full_matrix().

**Example Data**

Let’s assume you have the following files from a typical 10X dataset:

matrix.mtx.gz — the count matrix in Matrix Market format

features.tsv.gz — a list of gene IDs (rows)

barcodes.tsv.gz — a list of cell barcodes (columns)

```{r}
library(Matrix)
library(data.table)

matrix_file <- "matrix.mtx.gz"
features_file <- "features.tsv.gz"
barcodes_file <- "barcodes.tsv.gz"

```

## Read the Data

Use the main function `read_full_matrix()` to convert your files into a usable data.table:

```{}
{r, eval = FALSE}
dt <- read_full_matrix("matrix.mtx.gz", "features.tsv.gz", "barcodes.tsv.gz")

dt[1:5,1:5]

```
